---
title: "Evaluations of positive and negative stimuli using the Affective Misattribution Procedure (AMP) and self-reports"
subtitle: "Data processing"
author: "Template: Ian Hussey; content: Nadia Almeida Ferreira"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

# Dependencies

```{r}
install.packages("readr")
install.packages("janitor")
install.packages("stringr")

library(dplyr) # ?dplyr gives you the information 
library(tidyr)
library(readr)
library(janitor) # for clean_names()
library(stringr)

```

# Get data

```{r}

# demographics
data_demographics_raw_messy <- 
  read_csv("../data/raw/data_demographics_raw_messy.csv", skip = 2) |>
  janitor::clean_names()

data_demographics_raw <- read_csv("../data/raw/data_demographics_raw.csv") |>
  janitor::clean_names()

# self report measure
data_selfreport_raw <- read_csv("../data/raw/data_selfreport_raw.csv") |>
  janitor::clean_names()

# affect attribution procedure
data_amp_raw <- read_csv("../data/raw/data_amp_raw.csv") |>
  janitor::clean_names()

```

# Demographics

Clean the demographics data so that summaries of age and gender can be made in the analysis.

```{r}

# %>% tidyverse one -> control +shift+ m 

# |# > base R version -> pipe adds every code assigned to the same data set, treats output of one as the input of the other

# dat_age_gender <- data_demographics_raw |> select(subject, trialcode, response) #select puts only the columns that you specify 

dat_age_gender <- data_demographics_raw |> 
  rename(unique_id = subject, item = trialcode) |>
  select(unique_id, item, response)

# temp <- dat_age_gender |>
  #filter(item == "age") #no object sondern string that's why "age" and not just age

# there are much more felxible ways of doing 'string matching?
# temp <- dat_age_gender |>
  #filter(item %in% c("age", "AGE", "Age"))

# | #or operator
# & # and operator


dat_age_gender <- data_demographics_raw |> 
  rename(unique_id = subject, item = trialcode) |> #rename for clarity
  select(unique_id, item, response) |> #select useful columns
  filter(item == "age") #only show "age" rows of the "item" column

temp <- dat_age_gender |>
  distinct(response) # to show the unique responses

temp2 <- dat_age_gender |>
  mutate(response =str_remove_all(response, "\\D"))  #create or change variables

#check data type for each column 
 sapply(dat_age_gender, class)
 
 dat_age_gender <- data_demographics_raw |> 
  rename(unique_id = subject, item = trialcode) |> #rename for clarity
  select(unique_id, item, response) |> #select useful columns
  filter(item == "age") |>
  mutate(response = str_remove_all(response, "\\D"), 
         response = na_if(response, ""),
         response = as.numeric(response)) 
 
 #create modified data for gender 
 dat_g_temp <- data_demographics_raw |>
   rename(unique_id = subject, item = trialcode) |>
   select(unique_id, item, response) |>
   filter(item == "gender") |>
   mutate(response = str_remove_all(response, "\\d"),
          response = na_if(response, ""),
          response = as.factor(response),
          response = case_when(
            tolower(response) %in% c("Male", "male", "MALE") ~ "male",
            tolower(response) %in% c("Female", "female", "FEMALE", "woman", "Woman") ~ "female",
            tolower(response) %in% c("non-binary", "non binary", "Non-Binary", "Non Binary") ~ "non-binary"))
 
 
```

# Exclusions / data quality

## AMP

Create an exclusion variable `exclude_amp_performance` based on AMP performance: "exclude" if more than 10% of trials are < 100ms, or "include" if not.

Create an exclusion variable `exclude_amp_completeness` based on the AMP having the right number of trials.

```{r}

#data_amp_performance_criteria <- data_amp_raw 

```

# Self-reports

Create a mean score for each participant of the three self-report items.

```{r}

#data_selfreport_trial_level <- data_selfreport_raw 

```

# Affect Misattribution Procedure

Create an overall AMP bias score. Score each trial as having been evalauted as congruent with the prime or not. eg When trialcode == "prime_positive" & evaluative_response == 1, then record as 1, etc. AMP score is the proportion of congruent responses.

```{r}

#data_amp_score_congruence <- data_amp_raw 

```

# Combine 

Combine data frames together to create one wide-format data frame where each row represents a participant.

Flag all duplicates for exclusion.

```{r}

# data_processed_before_exclusions 

```

# Define master exclusion variable

```{r}

#data_processed <- data_processed_before_exclusions

```

# Write to disk

```{r}

# # in case this dir doesn't exist, create it
# dir.create("../data/processed/")
# 
# # save data to disk in that dir
# write_csv(data_processed, "../data/processed/data_processed.csv")

```

# Session info

```{r}

sessionInfo()

```


